Experiments with Housing Data

### 2022-07-29 dev/notebooks/housing.qmd
more work on gravitational generator. It works as expected if we choose strict convergence: we consider concergence as when the probability threshold is reached AND the reduction in our loss function from one iteration to another is small.

```{julia}
using AlgorithmicRecourseDynamics.Models
# Data:
data_train, data_test = Models.train_test_split(data)
n_epochs=100
map!(model -> Models.train(model, data_train; n_epochs=n_epochs, data_loader=data_loader), values(models))

```

>>>>

```{julia}
using AlgorithmicRecourseDynamics.Models
# Data:
data_train, data_test = Models.train_test_split(data)
n_epochs=100
map!(model -> Models.train(model, data_train; n_epochs=n_epochs, data_loader=data_loader), values(models))
initial_model_scores = [(name,Models.model_evaluation(model,data_train),Models.model_evaluation(model,data_test)) for (name,model) in pairs(models)]
```
